\let\pdfcreationdate=\creationdate
\documentclass[9pt,a4paper]{juicv}
\geometry{left=1.25cm, right=1.25cm, top=1.5cm, bottom=1.5cm, columnsep=1cm}
\usepackage{paracol}
\usepackage[newcommands]{ragged2e}

\newcommand{\myphone}{\href{tel:+440000000000}{+44 00 0000 0000}}
\newcommand{\myemail}{\href{mailto:job@igr.mk}{job@igr.mk}}
\IfFileExists{override.ignore.tex}{\input{override.ignore.tex}}{}

\hypersetup{colorlinks, urlcolor=accentColor}
\columnratio{0.73}

\setromanfont{Inter}[
    Extension      = .otf,
    UprightFont    = *-Regular,
    BoldFont       = *-Bold,
    ItalicFont     = *-Italic,
    BoldItalicFont = *-BoldItalic]

\begin{document}
\begin{paracol}{2}
\cvHeader
    {Igor Mikushkin}
    {}
    {Lead Software Engineer, Software Architect, CTO}

\setlength{\parskip}{0.7em}

Dear Hiring Team at Acme Bank,

I am excited to apply for the Lead Software Engineer position
within the banking platform team.
With my extensive experience in the tech industry
and hands-on expertise in designing scalable, secure systems,
I am eager to contribute to the development
of your next-generation core banking platform.

At Start From Today, I led the development of a talent platform,
which now has over 20,000 monthly active users.
I refined our Scrum processes, significantly improving the precision of estimations,
clarity of tasks, and effectiveness of testing.
My role involved leading a cross-functional team
and architecting a scalable, microservices-based system.
I wrote code as a hands-on developer,
managed the Google Cloud Platform infrastructure,
and promoted CI/CD practices throughout the development lifecycle.

During this project, I effectively coordinated team efforts
and cultivated a collaborative work environment.
This experience closely aligns with the responsibilities
of the Lead Software Engineer position at Acme Bank,
particularly in system architecture and team leadership.

Previously, as a Software Engineer at CQG Inc.,
I developed C++ microservices to integrate financial exchanges into our data feed,
achieving sub-100 microsecond latency in co-located environments.
This experience enhanced my expertise
in low-latency systems and performance optimisation
--- skills that could prove valuable in developing high-performance banking software.

Your focus on cloud-native technologies
and scalable microservices aligns perfectly with my background.
I have significant experience developing
and deploying distributed systems in Google Cloud,
and my technical toolkit includes Python, Go, Kubernetes, and CI/CD pipelines
--- all integral to your goals.

Python has been a cornerstone of my programming repertoire since 2008
when I used it for gathering depth of market data from feeds.
This demonstrated the value of automation in engineering workflows.
Since then, even if Python isn't the main language of a project,
I continue to use it for auxiliary tasks in all projects.

Since 2017, I have been actively engaged in personal projects using Go.
I appreciate this language for its simplicity, consistently clear code,
and excellent suitability for containerisation.

What excites me about this opportunity is the chance
to collaborate with your fintech partner, explore their best practices,
and apply them to a globally impactful banking platform.
As an enthusiastic learner with an engineering mindset,
a passion for building robust systems, and strong interpersonal skills,
I am confident in my ability to contribute meaningfully to your team.
Moreover, my keen attention to detail and analytical thinking should prove instrumental
in assimilating and implementing the best practices of your fintech partner.

I welcome the opportunity to discuss how my experience
aligns with Acme Bank's objectives.
Thank you for considering my application.

\vspace{12pt}

Best regards,\\
Igor Mikushkin

\newpage
\switchcolumn
\raggedright
\setlength{\parskip}{0em}

\cvRightSection{To}
    Acme Bank

\cvRightSection{From}
    Igor Mikushkin\\
    London, United Kingdom, SE8\\
    \myphone\\
    \myemail

    \vspace{6pt}
    {
        \small
        \href{https://linkedin.com/in/igrmk}{https://linkedin.com/in/igrmk}\\
        \href{https://github.com/igrmk}{https://github.com/igrmk}\\
        \href{https://coursera.org/learner/igrmk}{https://coursera.org/learner/igrmk}
        \par
    }

\end{paracol}

\end{document}
